---
title: "nycAirQualitySimpleLinearRegression"
author: "ACW"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

### Use R to answer Simple Linear Regression Questions about NYC air quality dataset

First step we will load the data and make a scatter plot

```{r}
airq <- airquality

#Scatter Plot
# Plot the data and the regression line
ggplot(airq, aes(x = Wind, y = Temp)) +
  geom_point() + # Scatter plot of the data
  geom_smooth(method="lm", col = "blue") + # Regression line
  labs(title = "Linear Regression Example", x = "Response Variable (Wind)", y = "Explanatory Variable (Temp)")

```

```{r}
model <- lm(Temp ~ Wind, data = airq)
#Forumula gives you the intercept and the slope
#= 90.13-1.23*x
```

Use this equation to predict the temperature, on a day when the observed wind speed is 8mph

```{r}
obs_wind_spped_8 <- 90.13 - 1.23*8
print(obs_wind_spped_8)
```

##Determine the Residual at a Given Observation We want to determine the residual at wind of 8mph and temp of 72°Fahrenheit

```{r, ehco=FALSE}
summary(model)
```

### Result 

The model provides an extremely small p-value for the slope of Wind, which is much smaller than the typical significance level (e.g., 0.05). This indicates that we can reject the null hypothesis that there is no relationship between Wind and Temp. Therefore, our data suggests that there is a statistically significant relationship between Wind and Temp.

```{r}
par(mfrow=c(2,2))
plot(model)
```

### Residuals Explained

Residuals are the difference between the observed value and the predicted value, visualized using various diagnostic plots. These include the Residuals vs. Fitted plot, the Q-Q plot for normality assessment, the Scale-Location plot to check homoscedasticity, and the Residuals vs. Leverage plot to identify influential data points.
